---
title: "RWorksheet#5a"
author: "Condag, Gagante, and Gonzaga"
date: "2024-11-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Extracting IMDB.
1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the tv show, tv rating, the number of people who voted, the number of episodes, the year it was released.

```{r}
library(polite)

polite::use_manners(save_as = 'polite_scrape.R')

url <- 'https://www.imdb.com/chart/top/?ref_=nv_mv_250&sort=rank%2Casc'

session <- bow(url,
               user_agent = "Educational")
session
```

```{r}
library(rvest)
library(dplyr)
library(httr)

title_list2 <- scrape(session) %>%
  html_nodes('h3.ipc-title__text') %>%
  html_text()

title_list_sub <- as.data.frame(title_list2[2:26])
colnames(title_list_sub) <- "Ranks"

split_df <- strsplit(as.character(title_list_sub$Ranks), ".", fixed = TRUE)
split_df <- data.frame(do.call(rbind, split_df))
colnames(split_df) <- c("Ranks", "Title")
titleAndRank <- data.frame(split_df)

ratings <- scrape(session) %>%
  html_nodes('span.ipc-rating-star--rating') %>%
  html_text()

if (length(ratings) < nrow(titleAndRank)) {
  ratings <- c(ratings, rep(NA, nrow(titleAndRank) - length(ratings)))
}
ratingsDf <- data.frame(ratings)

numberOfPeopleVoted <- scrape(session) %>%
  html_nodes('span.ipc-rating-star--voteCount') %>%
  html_text()

cleanedVotes <- gsub('[()]', '', numberOfPeopleVoted)

if (length(cleanedVotes) < nrow(titleAndRank)) {
  cleanedVotes <- c(cleanedVotes, rep(NA, nrow(titleAndRank) - length(cleanedVotes)))
}
cleanedVotesDf <- data.frame(cleanedVotes)

numEpisodes <- scrape(session) %>%
  html_nodes('span.sc-5bc66c50-6.OOdsw.cli-title-metadata-item:nth-of-type(2)') %>%
  html_text()

if (length(numEpisodes) < nrow(titleAndRank)) {
  numEpisodes <- c(numEpisodes, rep(NA, nrow(titleAndRank) - length(numEpisodes)))
}
numEpisodesDf <- data.frame(numEpisodes)

Year <- scrape(session) %>%
  html_nodes('span.sc-5bc66c50-6.OOdsw.cli-title-metadata-item:nth-of-type(1)') %>%
  html_text()

if (length(Year) < nrow(titleAndRank)) {
  Year <- c(Year, rep(NA, nrow(titleAndRank) - length(Year)))
}
YearDf <- data.frame(Year)

topShows <- cbind(titleAndRank, ratingsDf, cleanedVotesDf, numEpisodesDf, YearDf)

topShows
```

B. It will also include the number of user reviews and the number of critic reviews, as well as the popularity rating for each tv shows.
```{r}
homePage <- 'https://www.imdb.com/chart/toptv/'
mainPage <- read_html(homePage)

links <- mainPage %>%
  html_nodes("a.ipc-title-link-wrapper") %>%
  html_attr("href")

showInfo <- lapply(links, function(link) {
  fullLink <- paste0("https://imdb.com", link)

  userRevLink <- read_html(fullLink)
  userRevPageLink <-  userRevLink  %>%
    html_nodes('a.isReview') %>%
    html_attr("href")
  
  criticRev <- userRevLink %>%
              html_nodes("span.score") %>%
              html_text()
  criticDf <- data.frame(Critic_Reviews = criticRev[2], stringsAsFactors = FALSE)
  
  popularityRating <-  userRevLink %>%
              html_nodes('[data-testid="hero-rating-bar__popularity__score"]') %>%
              html_text()
  
  userRev <- read_html(paste0("https://imdb.com",  userRevPageLink[1]))
  userRevCount <- userRev %>%
    html_nodes('[data-testid="tturv-total-reviews"]') %>%
    html_text()

  return(data.frame(User_Reviews = userRevCount, Critic = criticDf, Popularity_Rating = popularityRating)) 
})


showUrlDf <- do.call(rbind, showInfo)
showUrlDf

allShows <- cbind(topShows, showUrlDf)
allShows 
```

2. From the 50 tv shows, select at least 5 tv shows to scrape 20 user reviews that will include the reviewer’s name, date of reviewed, user rating, title of the review, the numbers for “is helpful” and “is not helpful”, and text reviews.
```{r}
library(rvest)
library(dplyr)

urlsOfFiveShows <- c(
  "https://www.imdb.com/title/tt0903747/reviews/?ref_=ttexr_ql_2",
  "https://www.imdb.com/title/tt5491994/reviews/?ref_=tt_ov_ql_2",
  "https://www.imdb.com/title/tt0185906/reviews/?ref_=tt_ov_ql_2",
  "https://www.imdb.com/title/tt7366338/reviews/?ref_=tt_ov_ql_2",
  "https://www.imdb.com/title/tt0944947/reviews/?ref_=tt_ov_ql_2"
)

fiveShowsUrlDf <- data.frame(
  Title = c(
    "Breaking Bad",
    "Planet Earth II",
    "Band of Brothers",
    "Chernobyl", 
    "Game of Thrones"
  ),
  URLs = urlsOfFiveShows
) 

scrapeReviews <- function(show_url) {
  page <- read_html(show_url)
  
  userNames <- page %>%
    html_nodes('[data-testid="author-link"]') %>%
    html_text()
  
   reviewDates <- page %>%
    html_nodes('li.review-date') %>%
    html_text()
   
     userRating <- page %>%
    html_nodes('span.ipc-rating-star--rating') %>%
    html_text()

     revTitle <- page %>%
    html_nodes('h3.ipc-title__text') %>%
    html_text()
     
     helpfulRev <- page %>%
    html_nodes('span.count--up') %>%
    html_text()
     
      notHelpful <- page %>%
    html_nodes('span.count--down') %>%
    html_text()
    
       data.frame(Usernames = head(userNames, 20), Dates = head(reviewDates, 20), userRating = head(userRating, 20), Review_Title = head(revTitle, 20))
}

reviews_data <- lapply(fiveShowsUrlDf$URLs, scrapeReviews)
names(reviews_data) <- fiveShowsUrlDf$Title
reviews_data[["Breaking Bad"]]
reviews_data[["Planet Earth II"]]
reviews_data[["Band of Brothers"]]
reviews_data[["Chernobyl"]]
reviews_data[["Game of Thrones"]]
```

3.
```{r}
library(ggplot2)
years <- substr(Year, 1,4)
years <- as.numeric(Year)      

ggplot(data.frame(Year = years), aes(x = Year)) +
  geom_line(stat = "count", fill = "pink", color = "purple") +
  labs(title = "Number of TV Shows Released by Year",
       x = "Year",
       y = "Number of TV Shows") +
  theme_minimal()

mostShowsYear <- as.data.frame(table(Year))
mostShowsYear <- mostShowsYear[which.max(mostShowsYear$Freq), ]
print(mostShowsYear)
```

4 and 5. Select 5 categories from Amazon and select 30 products from each category. Extract the price, description, ratings and reviews of each product.
```{r}
library(httr)
library(polite)
library(rvest)

polite::use_manners(save_as = 'polite_scrape.R')

url <- 'https://www.amazon.com/'


session <- bow(url,
               user_agent = "Educational")
session
```

# Shoes Category
```{r}
shoes_url <- 'https://www.amazon.com/s?i=specialty-aps&bbn=16225020011&rh=n%3A7141123011%2Cn%3A16225020011%2Cn%3A679217011&ref=nav_em__nav_desktop_sa_intl_shoes_0_2_14_3'

scrape_shoes <- function(url, category) {
  page <- read_html(url)
  
  product_titles <- page %>%
    html_nodes("h2.a-size-mini") %>% 
    html_text(trim = TRUE)

  price <- page %>% 
    html_nodes(".a-price .a-offscreen") %>% 
    html_text(trim = TRUE)
  
  ratings <- page %>% 
    html_nodes("span.a-icon-alt") %>% 
    html_text(trim = TRUE)
  
  review <- page %>% 
    html_nodes("div.a-sectionr-celwidget") %>% 
    html_text(trim = TRUE)
  
  data.frame(
    Product_titles = product_titles[1:30],
    Price = price[1:30],
    Ratings = ratings[1:30],
    Review = review[1:30]
  )
}

shoes_products <- scrape_shoes(shoes_url, "Shoes")
shoes_products
```

# Makeup Category
```{r}
makeup_url <- 'https://www.amazon.com/s?i=specialty-aps&bbn=16225006011&rh=n%3A%2116225006011%2Cn%3A11058281&'

scrape_makeup <- function(url, category) {
  page <- read_html(url)
  
  product_titles <- page %>%
    html_nodes("h2.a-size-mini") %>% 
    html_text(trim = TRUE)

  price <- page %>% 
    html_nodes(".a-price .a-offscreen") %>% 
    html_text(trim = TRUE)
  
  ratings <- page %>% 
    html_nodes("span.a-icon-alt") %>% 
    html_text(trim = TRUE)
  
  review <- page %>% 
    html_nodes("span.a-size-base.review-text") %>% 
    html_text(trim = TRUE)
  
  data.frame(
    Product_titles = product_titles[1:30],
    Price = price[1:30],
    Ratings = ratings[1:30],
    Review = review[1:30]
  )
}

makeup_products <- scrape_makeup(makeup_url, "Makeup")
makeup_products
```

# Jewelry Category
```{r}
jewelry_url <- 'https://www.amazon.com/s?i=specialty-aps&bbn=16225018011&rh=n%3A7141123011%2Cn%3A16225018011%2Cn%3A7192394011&ref=nav_em__nav_desktop_sa_intl_jewelry_0_2_12_4'

scrape_jewelry <- function(url, category) {
  page <- read_html(url)
  
  product_titles <- page %>%
    html_nodes("h2.a-size-mini") %>% 
    html_text(trim = TRUE)

  price <- page %>% 
    html_nodes(".a-price .a-offscreen") %>% 
    html_text(trim = TRUE)
  
  ratings <- page %>% 
    html_nodes("span.a-icon-alt") %>% 
    html_text(trim = TRUE)
  
  review <- page %>% 
    html_nodes("span.a-size-base.review-text") %>% 
    html_text(trim = TRUE)
  
  data.frame(
    Product_titles = product_titles[1:30],
    Price = price[1:30],
    Ratings = ratings[1:30],
    Review = review[1:30]
  )
}

jewelry_products <- scrape_jewelry(jewelry_url, "Jewelry")
head(jewelry_products, 30)
```

# Girls_Clothing Category
```{r}
girls_clothing_url <- 'https://www.amazon.com/s?i=specialty-aps&bbn=16225020011&rh=n%3A7141123011%2Cn%3A16225020011%2Cn%3A1040664&ref=nav_em__nav_desktop_sa_intl_clothing_0_2_14_2'

scrape_girls_clothing <- function(url, category) {
  page <- read_html(url)
  
  product_titles <- page %>%
    html_nodes("h2.a-size-mini") %>% 
    html_text(trim = TRUE)

  price <- page %>% 
    html_nodes(".a-price .a-offscreen") %>% 
    html_text(trim = TRUE)
  
  ratings <- page %>% 
    html_nodes("span.a-icon-alt") %>% 
    html_text(trim = TRUE)
  
  review <- page %>% 
    html_nodes("span.a-size-base.review-text") %>% 
    html_text(trim = TRUE)
  
  data.frame(
    Product_titles = product_titles[1:30],
    Price = price[1:30],
    Ratings = ratings[1:30],
    Review = review[1:30]
  )
}

girls_clothing_products <- scrape_girls_clothing(girls_clothing_url, "Girls_Clothing")
head(girls_clothing_products, 30)
```

# BabyToys Category
```{r}
babytoys_url <- 'https://www.amazon.com/s?i=specialty-aps&bbn=16225005011&rh=n%3A%2116225005011%2Cn%3A196601011&ref=nav_em__nav_desktop_sa_intl_baby_toddler_toys_0_2_10_4'

scrape_babytoys <- function(url, category) {
  page <- read_html(url)
  
  product_titles <- page %>%
    html_nodes("h2.a-size-mini") %>% 
    html_text(trim = TRUE)

  price <- page %>% 
    html_nodes(".a-price .a-offscreen") %>% 
    html_text(trim = TRUE)
  
  ratings <- page %>% 
    html_nodes("span.a-icon-alt") %>% 
    html_text(trim = TRUE)
  
  review <- page %>% 
    html_nodes("span.a-size-base.review-text") %>% 
    html_text(trim = TRUE)
  
  data.frame(
    Product_titles = product_titles[1:30],
    Price = price[1:30],
    Ratings = ratings[1:30],
    Review = review[1:30]
  )
}

babytoys_products <- scrape_babytoys(babytoys_url, "Babytoys")
head(babytoys_products, 30)
```

6. Describe the data you have extracted.
  - We extracted 30 products for each category from amazon. The categories that we chose are shoes, makeups, jewelry, girls' clothing, and babytoys. For each categories, we extracted 30 product titles, price, rating and reviews that is shown inside a data frame.
  
7. What will be your use case for the data you have extracted?
  - The use case for the data extacted is trend analysis.
  
8. Create graphs regarding the use case. And briefly explain it.
```{r}
library(ggplot2)

shoes_data <- data.frame(Date = c('2024-01-01', '2024-02-01', '2024-03-01'),
                        Avg_Price = c(50, 55, 53))
shoes_data$Date <- as.Date(shoes_data$Date)

ggplot(shoes_data, aes(x = Date, y = Avg_Price)) +
  geom_line() +
  geom_point() +
  labs(title = "Average Price Trend for Shoes Over Time", x = "Date", y = "Average Price")
```
  - The Trend Analysis graph tracks changes in a key metric (e.g., average price) over time. The x-axis shows the time period (like months), while the y-axis shows the value of the metric. For example, a graph could show the average price of shoes increasing from $50 in January to $55 in February, then dropping to $53 in March. This helps identify patterns, like price fluctuations, and informs decisions on when prices might rise or fall, aiding in pricing strategies and market forecasting.
  
9. Graph the price and the ratings for each category. Use basic plotting functions and ggplot2 package.

# Shoes Category
```{r}
library(dplyr)
library(ggplot2)

shoes_products$Price <- as.numeric(gsub("[^0-9.]", "", shoes_products$Price))
shoes_products$Ratings <- as.numeric(gsub("[^0-9.]", "", shoes_products$Ratings))

shoes_price_ratings <- function(data, category_name) {
  ggplot(data, aes(x = Price, y = Ratings)) +
    geom_point(color = "blue") +  
    geom_smooth(method = "lm", se = FALSE, color = "red") +  
    theme_minimal() +
    labs(title = paste("Price vs Ratings for", category_name), 
         x = "Price", 
         y = "Ratings") +  
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

shoes_price_ratings(shoes_products, "Shoes")
```

# Makeup Category
```{r}
library(dplyr)
library(ggplot2)

makeup_products$Price <- as.numeric(gsub("[^0-9.]", "", makeup_products$Price))
makeup_products$Ratings <- as.numeric(gsub("[^0-9.]", "", makeup_products$Ratings))

makeup_price_ratings <- function(data, category_name) {
  ggplot(data, aes(x = Price, y = Ratings)) +
    geom_point(color = "coral1") +  
    geom_smooth(method = "lm", se = FALSE, color = "chocolate4") +  
    theme_minimal() +
    labs(title = paste("Price vs Ratings for", category_name), 
         x = "Price", 
         y = "Ratings") +  
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

makeup_price_ratings(makeup_products, "Shoes")
```
# Jewelry Category
```{r}
library(dplyr)
library(ggplot2)

jewelry_products$Price <- as.numeric(gsub("[^0-9.]", "", jewelry_products$Price))
jewelry_products$Ratings <- as.numeric(gsub("[^0-9.]", "", jewelry_products$Ratings))

jewelry_price_ratings <- function(data, category_name) {
  ggplot(data, aes(x = Price, y = Ratings)) +
    geom_point(color = "purple") +  
    geom_smooth(method = "lm", se = FALSE, color = "darkblue") +  
    theme_minimal() +
    labs(title = paste("Price vs Ratings for", category_name), 
         x = "Price", 
         y = "Ratings") +  
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

jewelry_price_ratings(jewelry_products, "Jewelry")

```

# Girl's Clothing Category
```{r}
library(dplyr)
library(ggplot2)

girls_clothing_products$Price <- as.numeric(gsub("[^0-9.]", "", girls_clothing_products$Price))
girls_clothing_products$Ratings <- as.numeric(gsub("[^0-9.]", "", girls_clothing_products$Ratings))

girls_clothing_price_ratings <- function(data, category_name) {
  ggplot(data, aes(x = Price, y = Ratings)) +
    geom_point(color = "pink") +  
    geom_smooth(method = "lm", se = FALSE, color = "deeppink4") +  
    theme_minimal() +
    labs(title = paste("Price vs Ratings for", category_name), 
         x = "Price", 
         y = "Ratings") +  
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

girls_clothing_price_ratings(girls_clothing_products, "Girls' Clothing")

```

# Baby Toys Category
```{r}
library(dplyr)
library(ggplot2)

babytoys_products$Price <- as.numeric(gsub("[^0-9.]", "", babytoys_products$Price))
babytoys_products$Ratings <- as.numeric(gsub("[^0-9.]", "", babytoys_products$Ratings))

babytoys_price_ratings <- function(data, category_name) {
  ggplot(data, aes(x = Price, y = Ratings)) +
    geom_point(color = "green") +  
    geom_smooth(method = "lm", se = FALSE, color = "darkgreen") +  
    theme_minimal() +
    labs(title = paste("Price vs Ratings for", category_name), 
         x = "Price", 
         y = "Ratings") +  
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

babytoys_price_ratings(babytoys_products, "Baby Toys")

```

10. Rank the products of each category by price and ratings. Explain briefly.

```{r}
rank_products <- function(data, shoes_products) {
  data <- data %>%
    mutate(
      Price = as.numeric(gsub("[^0-9.]", "", Price)),
      Ratings = as.numeric(gsub("[^0-9.]", "", Ratings))
    ) %>%
    mutate(
      Rank_by_Price = rank(-Price, ties.method = "min"),
      Rank_by_Ratings = rank(-Ratings, ties.method = "min")
    ) %>%
    arrange(Rank_by_Price) %>%
    select(Product_titles, Price, Ratings, Rank_by_Price, Rank_by_Ratings) %>%
    head(10)
}

shoes_ranked <- rank_products(shoes_products, "Shoes")
print("Top 10 Shoes by Price and Ratings")
print(shoes_ranked)

makeup_ranked <- rank_products(makeup_products, "Makeup")
print("Top 10 Makeup Products by Price and Ratings")
print(makeup_ranked)

jewelry_ranked <- rank_products(jewelry_products, "Jewelry")
print("Top 10 Jewelry Products by Price and Ratings")
print(jewelry_ranked)

girls_clothing_ranked <- rank_products(girls_clothing_products, "Girl's Clothing")
print("Top 10 Girl's Clothing Products by Price and Ratings")
print(girls_clothing_ranked)

babytoys_ranked <- rank_products(babytoys_products, "Baby Toys")
print("Top 10 Baby Toys Products by Price and Ratings")
print(babytoys_ranked)
```

```{r}
# Shoes - Price Ranking
plot_rankings <- function(data, shoes_ranked, rank_col, value_col, value_name) {
  ggplot(data, aes(x = reorder(Product_titles, -!!sym(value_col)), y = !!sym(value_col), fill = !!sym(value_col))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(
      title = paste("Top 10", shoes_ranked, "by", value_name),
      x = "Product Titles",
      y = value_name
    ) +
    theme_minimal()
}

plot_rankings(shoes_ranked, "Shoes", "Rank_by_Price", "Price", "Price")
```
```{r}
# Makeup - Price Ranking
plot_rankings <- function(data, makeup_ranked, rank_col, value_col, value_name) {
  ggplot(data, aes(x = reorder(Product_titles, -!!sym(value_col)), y = !!sym(value_col), fill = !!sym(value_col))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(
      title = paste("Top 10", makeup_ranked, "by", value_name),
      x = "Product Titles",
      y = value_name
    ) +
    theme_minimal()
}

plot_rankings(makeup_ranked, "Makeup", "Rank_by_Price", "Price", "Price")
```
```{r}
# Jewelry - Price Ranking
plot_rankings <- function(data, jewelry_ranked, rank_col, value_col, value_name) {
  ggplot(data, aes(x = reorder(Product_titles, -!!sym(value_col)), y = !!sym(value_col), fill = !!sym(value_col))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(
      title = paste("Top 10", jewelry_ranked, "by", value_name),
      x = "Product Titles",
      y = value_name
    ) +
    theme_minimal()
}

plot_rankings(jewelry_ranked, "Jewelry", "Rank_by_Price", "Price", "Price")
```
```{r}
# Girl’s Clothing - Price Ranking
plot_rankings <- function(data, girls_clothing_ranked, rank_col, value_col, value_name) {
  ggplot(data, aes(x = reorder(Product_titles, -!!sym(value_col)), y = !!sym(value_col), fill = !!sym(value_col))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(
      title = paste("Top 10", girls_clothing_ranked, "by", value_name),
      x = "Product Titles",
      y = value_name
    ) +
    theme_minimal()
}

plot_rankings(girls_clothing_ranked, "Girl's Clothing", "Rank_by_Price", "Price", "Price")
```

```{r}
# Baby Toys - Price Ranking
plot_rankings <- function(data, babytoys_ranked, rank_col, value_col, value_name) {
  ggplot(data, aes(x = reorder(Product_titles, -!!sym(value_col)), y = !!sym(value_col), fill = !!sym(value_col))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(
      title = paste("Top 10", babytoys_ranked, "by", value_name),
      x = "Product Titles",
      y = value_name
    ) +
    theme_minimal()
}

plot_rankings(babytoys_ranked, "Baby Toys", "Rank_by_Price", "Price", "Price")

```

